Deployable Probabilistic Programming

### 2019-04-23 paper/paper.tex
stan times

\begin{table*}
\begin{tabular}{r | c |  c | c | c | c | c | }
	{\it model}  & \multicolumn{6}{c|}{\it time} \\
	& \multicolumn{3}{c|}{\it compilation} & \multicolumn{3}{c|}{\it execution} \\
	& Infergo & Turing & Stan & Infergo & Turing & Stan \\\hline
	8 schools              & 0.5s & & & 0.6s  & & \\
	10D normal, 100 points & 0.5s & & & 3.0s  & & \\
	50D normal, 100 points & 0.5s & & & 13.0s & & \\
	LDA, 262 words, 25 docs
	                       & 0.6s & & &       & & 
\end{tabular}
\caption{Compilation and execution times for 1000 iterations 
	of HMC with 10 leapfrog steps.}
\label{tab:memory-runtime}
\end{table*}

>>>>

\begin{table*}
	\begin{tabular}{r | c |  c | c | c | c | c | }
		{\it model}   & \multicolumn{6}{c|}{\it time, seconds} \\
					  & \multicolumn{3}{c|}{\it compilation} & \multicolumn{3}{c|}{\it execution} \\
					  & Infergo & Turing & Stan              & Infergo & Turing & Stan    \\\hline
		Eight schools & 0.5     &        & 50                & 0.6     &        & 0.12    \\
		GMM           & 0.5     &        & 55                & 3.0     &        & 4.9     \\
		LDA           & 0.5     &        & 55                &         &        & 3.7     \\ 
	\end{tabular}
\caption{Compilation and execution times for 1000 iterations 
	of HMC with 10 leapfrog steps.}
\label{tab:memory-runtime}
\end{table*}
